paper1_results_figs_slimmed_50_rr

### 2016-06-17 inst/documents/paper1_results_figs_rr.Rmd
rr_advantage

  #nScenarios <- 10  
  #nScenarios <- 100
  #nScenarios <- 500 
  nScenarios <- 1000
  #nScenarios <- 10000

@@

  ## save results objects as rda for re-use
  save(listOutMix, file=paste0(outFolder,'listOutMix_rr_1000.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_rr_1000.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_rr_1000.rda'))  
```

@@

  ## to load previously saved runs  
  load(file=paste0(outFolder,'listOutMix_rr_1000.rda'))
  load(file=paste0(outFolder,'listOutI1_rr_1000.rda'))
  load(file=paste0(outFolder,'listOutI2_rr_1000.rda'))

>>>>

  #nScenarios <- 10  
  #nScenarios <- 100
  #nScenarios <- 500 
  #nScenarios <- 1000
  nScenarios <- 10000

@@

  ## save results objects as rda for re-use
  save(listOutMix, file=paste0(outFolder,'listOutMix_rr_10000.rda'))
  save(listOutI1, file=paste0(outFolder,'listOutI1_rr_10000.rda'))
  save(listOutI2, file=paste0(outFolder,'listOutI2_rr_10000.rda'))  
```

@@

  ## to load previously saved runs  
  load(file=paste0(outFolder,'listOutMix_rr_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_rr_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_rr_10000.rda'))

### 2016-06-17 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
rr_advantage

---
title: "paper1_results_figs_slimmed_50"
output: pdf_document
#output: word_document
author: "Andy South"
date: "`r Sys.Date()`"
---

## ALL FIGS AT 50% resistance threshold

## Main Figures for paper 1 : version 6 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed_50.Rmd

@@

  load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

  # load(file=paste0(outFolder,'listOutMix_unequal.rda'))
  # load(file=paste0(outFolder,'listOutI1_unequal.rda'))
  # load(file=paste0(outFolder,'listOutI2_unequal.rda'))

@@

  rownames(treeInput)[rownames(treeInput)=="s.RR1_A0"] <- "selection_coef_allele1"
  rownames(treeInput)[rownames(treeInput)=="s.RR2_0B"] <- "selection_coef_allele2"

@@

#curtis_f2 with P_1 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.49 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43, addCombinedStrategy=FALSE )

#curtis_f2 with P_2 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.49 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43, addCombinedStrategy=FALSE )

>>>>

---
title: "paper1_results_figs_slimmed_50_rr"
output: pdf_document
#output: word_document
author: "Andy South"
date: "`r Sys.Date()`"
---

## Figures for paper 1 : version 7

## using rr_advantage instead of selection coefficient

### automagically generated by R from paper1_results_figs_slimmed_50_rr.Rmd

@@

  ## to load previously saved runs  
  load(file=paste0(outFolder,'listOutMix_rr_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_rr_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_rr_10000.rda'))

  # load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  # load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  # load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

@@

  # 14/6/16
  # rownames(treeInput)[rownames(treeInput)=="s.RR1_A0"] <- "selection_coef_allele1"
  # rownames(treeInput)[rownames(treeInput)=="s.RR2_0B"] <- "selection_coef_allele2"

@@

#curtis_f2 with P_1 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.49 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_advantage_I1=0.23/0.73, rr_advantage_I2 = 0.43/1, addCombinedStrategy=FALSE )

#curtis_f2 with P_2 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.49 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_advantage_I1=0.23/0.73, rr_advantage_I2 = 0.43/1, addCombinedStrategy=FALSE )
